\section{Design or Architecture}
Change the heading of the section to make it more specific to match your thesis work. Avoid putting generic heading and titles. Find a unique and search engine index-able name for your project. A proper noun. For example, instead of just saying "Design", put "Design of Anubis: a Fault-Tolerant  Extendable File System". 

Design or architecture is a high-level concept and idea that you have developed or put together to solve the problem. These are kind of details which are important to re-do your design or project completely from scratch by others in a different setting or system than what you have used. This is the \textbf{"transferable knowledge"}. Use the appropriate terminology. Do not use colloquial lingo from the web to describe concepts. If you are unsure, check and read other research papers and pay attention to the language used. Whenever in doubt, ask us. 


$ $\\

\noindent\textbf{Important:} Do not write frivolous claims. Often in thesis I read "Idea X or design Y is simple" or "It is considered complex" or "everyone uses it". Please do not do this. Every such statement in your thesis should be backed up by a reference. If not, then it is risky to write such claims and you should avoid it. These claims are needed when you have to justify your design or architecture choice, why did you choose one style over other. In a scientific literature, why and justification is very important. Try to reason about your own thinking and working process and write it when describing a design. As usual, if not sure how to justify your choices, ask us. 


\subsection*{Can I copy images from the Internet?}

First, do not do it. It is often easy to redraw the image by yourself, thus side stepping the image copying issue. But if you must (very discouraged), then you must clearly attribute that picture as "copied from [...]". Make sure that the image is not copyrighted. Also, this is an exception not a rule. You need to make a very strong case for why you want to copy such an image instead of redrawing it. 
