\section*{Appendix A: Reproducibility (Mandatory)}
This is a mandatory appendix. You must include this in your thesis. This subsection can be designed around the ACM guidelines for experiment reproducibility at \url{https://www.acm.org/publications/policies/artifact-review-badging}. ACM offers badges in three classes: Artifacts Evaluated, Artifacts Available and Results Validated. Understand what they mean and provide sufficient information for someone completely new to take your code and run it on a new machine.  

The least I expect is a running code. Hence, you should clearly describe how to download, setup and run the code on a new machine. How to run a representative experiment that can verify if the software is working. And lastly, how to reproduce one of the key experiments from your thesis and reproduce the exact data and graphs. For more specific guidelines regarding what to include in this subsection, please see \url{https://ctuning.org/ae/checklist.html} and use the latex template provided here \url{https://github.com/ctuning/ck-artifact-evaluation/blob/master/wfe/artifact-evaluation/templates/ae.tex}. Fill in the relevant sections. 

I prefer that you make your code available on Github. A part of the documentation that you will write here can also be used in the top-level README.md file for your Github repo. Make sure no broken or private repo links are used. If you have used private repo to develop the code, then make sure to make it public before your thesis is completed. 

For data repositories you can consider \url{https://zenodo.org/}. For example, see this dataset from Cloud performance reproducibility experiments \url{https://zenodo.org/record/3576604}. 

\newpage 
\section*{Appendix B: Self Reflection}
Explain in this section how this research benefited yourself. How did this project develop you? How did it develop your career? Also include here quantitative elements: break down the time spent on this project by type of activity / element of the project.

\newpage 
\section*{Appendix C: Additional Experiments}
If you have additional experiments to report, you can include them here. 
